A thesis draft

### 2018-11-18 res/sections/26-TestsPerformance.tex
Change images of resilience tests and fix description

The receiver record the instant on which it receives a packet and, to emulate a
SF crash, we bring down the central link of the chain after 5 seconds using the
command \verb!kubectl delete pods <pod-id> --grace-period=0 --force!, to force
the stop of a pod.

We performed the test using both UDP and TCP protocols, repeating for each
protocol the measurement 20 times.
Figure~\ref{chap:tests:sec:fault:img:faultgraphudp} and
Figure~\ref{chap:tests:sec:fault:img:faultgraphtcp} represent the behavior of
the system in the worst case and in the best case measured, respectively for
UDP and TCP. The average interval of time in which the receiver does not
receive anything was 13.5793391228s in case of UDP, 13.7828050137s in case of
TCP. This is a good result, because in about 13s a machine can crash and can be
recreated and be operative again. We can also notice that there are no
significant difference between worst cases and best cases measured 
respectively 12.75 and 14.41 for UDP and 13.14 and 14.63 for TCP)

\begin{figure}[]
  %\centering
    \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[scale=0.3]{nolog_udp}
        \caption{Packet time arrival in case of SF fault using UDP}
        \label{chap:tests:sec:fault:img:faultgraphudp}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[scale=0.3]{nolog_tcp}
        \caption{Packet time arrival in case of SF fault using TCP}
        \label{chap:tests:sec:fault:img:faultgraphtcp}
    \end{subfigure}
    \caption{Comparison among TCP and UDP in terms of packet time arrival in
    case of SF fault}
    \label{chap:tests:sec:fault:img:faultgrapht}
\end{figure}

>>>>

In that test we bring down the central link of the chain after 5 seconds using
the command \verb!kubectl delete pods <pod-id> --grace-period=0 --force!, to
force the stop of a pod and we recorded the time on which packets arrived to
the receiver and passed through the VNF just before the one that will be make
stopped.

We performed the test using both UDP and TCP protocols, repeating for each
protocol the measurement 20 times.
Figure~\ref{chap:tests:sec:fault:img:faultgraphudp} and
Figure~\ref{chap:tests:sec:fault:img:faultgraphtcp} represent the behavior of
the system during the experiment: blue points describe packet inter-arrival
time on the receiver, green once the same metric on the SF that precede the
central one. The average interval of time in which the
receiver does not receive anything was 13.5793391228s in case of UDP,
13.7828050137s in case of TCP. This is a good result, because in about 13s a
machine can crash and can be recreated and be operative again.

\begin{figure}[]
  %\centering
    \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[scale=0.3]{udp_fault}
        \caption{Packet time arrival in case of SF fault using UDP}
        \label{chap:tests:sec:fault:img:faultgraphudp}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[scale=0.3]{tcp_fault}
        \caption{Packet time arrival in case of SF fault using TCP}
        \label{chap:tests:sec:fault:img:faultgraphtcp}
    \end{subfigure}
    \caption{Comparison among TCP and UDP in terms of packet time arrival in
    case of SF fault}
    \label{chap:tests:sec:fault:img:faultgrapht}
\end{figure}
